\documentclass[10pt,a4paper]{extarticle}
%\documentclass[]{file}
\usepackage[a4paper,margin = 0.3in]{geometry}
\usepackage{romannum}
\usepackage{mathtools} 
\usepackage{amsmath} 
\usepackage{fontawesome}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage[super]{nth}
% \usepackage[usenames,dvipsnames]{xcolor}
%...................rahul codes......................
\usepackage{lipsum}
\usepackage{enumitem}
\usepackage{color}
\newlength\boxwid%
\definecolor{mygrey}{rgb}{0.73, 0.73, 0.73}
\definecolor{lgrey}{rgb}{0.9, 0.9,0.9}
\let\oldtextbullet=\textbullet
\def\textbullet{%
    \settowidth{\boxwid}{\ \indent\oldtextbullet\ }%
    \hangindent=\boxwid%
    \oldtextbullet}
    \usepackage{marvosym,array,amsfonts}
\usepackage{array}              %% for adjusting column widths in table
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}     %% new column type
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}       %% new column type
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}      %% new column type
\usepackage{hyperref}
\setlength{\parindent}{0pt}	%% used for setting the no indentation at the beginning of the paragraph
\usepackage{multicol}
\newcommand{\tabitem}{\textbullet~~}
%......................................................
\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!50,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
    }
\begin{document}
\pagenumbering{gobble}
\begin{flushleft}
\noindent {\Huge\textbf{\sc{Deepanshu}}}
\end{flushleft}
\vspace{-4pt}
3rd Year Undergraduate  \hfill\href{mailto:deepanshu21@iitk.ac.in}{{\faEnvelope} deepanshu21@iitk.ac.in} \(|\) \href{tel:+917082575299}{ {\faPhone} +917082575299}\\
%\vspace{-2pt}
Department of Computer Science and Engineering \hfill\href{https://github.com/Deepanshu18099}{{\faGithub} Deepanshu18099} \(|\) \href{https://www.linkedin.com/in/deepanshu-yadav-65a1ab223/}{{\faLinkedin} deepanshu-yadav}
\vspace{-6pt}
\\
\vspace{-8pt}
\noindent\rule[0.5ex]{\linewidth}{1pt}
\vspace{-18pt}
{\large \textbf{\begin{tcolorbox}[colback=mygrey,height=6mm]\textsc{Academic Qualifications}\end{tcolorbox}}}
\vspace{-10pt}
\begin{center}
\begin{tabular}{|p{2.4cm}|p{4.2cm}|p{8.5cm}|p{1.8cm}|}
\hline
\centering{\textbf{Year}} & \centering{\textbf{Degree/Certificate}} & \centering{\textbf{Institute}} & \textbf{CPI/$\%$}\\
\hline
\centering{2021} - Present & \centering{B.Tech} & \centering{Indian Institute of Technology Kanpur} & 7.0/10\\
\hline
\centering{2021} & \centering{CBSE(\Romannum{12})} & \centering{Yaduvanshi Shiksha Niketan, Narnaul} & 89.8$\%$\\
\hline
\centering{2019} & \centering{CBSE(\Romannum{10})} & \centering{Yaduvanshi Shiksha Niketan, Narnaul} & 90.6$\%$
\\
\hline
\end{tabular}
\end{center}
\vspace{-1mm}
{\large \textbf{\begin{tcolorbox}[colback=mygrey,height=6mm]\textsc{Scholastic Achievements}\end{tcolorbox}}}
\vspace{-2.4mm}
\begin{itemize}
\item Secured \textbf{All India Rank 1040} in \textbf{JEE-Advanced 2021} among 1.4 Lakh candidates, Conducted by IIT Kharagpur.
\item Secured \textbf{All India Rank 2198} in \textbf{JEE-Mains 2021} among 10 lakh+ appeared candidates all over India.
\item Recipient of Excellence Scholarship from \textbf{National Talent Search Examination 2019} conducted by \textbf{NCERT}.
\item Secured \textbf{100 percentile} in \textbf{Physics} subject	 in \textbf{JEE-Mains 2021} by scoring a maximum possible score 100/100.
\item Among \textbf{State top 1\%} in \textbf{National Standard Examination In Junior Science 2018-2019} conducted by IAPT.
\end{itemize}

\medskip
\vspace{-8mm}

{\large \textbf{\begin{tcolorbox}[colback=mygrey,height=6mm]\textsc{Key Projects}\end{tcolorbox}}}

\vspace{-6mm}
{\begin{tcolorbox}[colback=lgrey,height=6mm]\textbf{
\href{https://github.com/atulyasndrm/Starbugs}{HealthPlusPlus {\faGithub}}}
{\(|\) CS253 Course Project}
\hfill \textit{(Jan'23-Apr'23)}
\end{tcolorbox}}
\vspace{-1.6mm}
\hspace{3mm}\textbf{Mentor}:\emph{ Prof. Indranil Saha (Computer Science and Engineering, IIT Kanpur)}
\begin{itemize}
\item  With a team of 10, Developed an \textbf{automated software} for \textbf{Health Center} of IITK providing its services online.
\item Used rapid development framework \textbf{Django} for back-end and its SQL database, \textbf{HTML, CSS, Javascript} for front-end.
\item Executed an end-to-end development process from \textbf{SRS} and \textbf{Design} document to \textbf{implementation} of automated parts.
\item Collaborated with another team for Beta Testing to identify and resolve the errors within both team’s application
\end{itemize}


\vspace{-1.6mm}
{\begin{tcolorbox}[colback=lgrey,height=6mm]\textbf{
\href{https://github.com/Deepanshu18099/CS220-Project}{CSE-Bubble Processor {\faGithub}}}
{\(|\) CS220 Course Project }
\hfill \textit{(Jan'23-Apr'23)}
\end{tcolorbox}}
\vspace{-2mm}
\hspace{3mm}\textbf{Mentor}:\emph{ Prof. Urbi Chatterjee (Computer Science and Engineering, IIT Kanpur)}
\begin{itemize}
\item Framed a single-cycle processor, including op-code design, data path implementation and control path development.
\item Implemented ALU in top-down approach to develop different modules for different types of instructions.
\item Implemented MIPS code for Bubble Sort, converting it to machine code and storing output in data memory.
\end{itemize}

\vspace{-1.6mm}
{\begin{tcolorbox}[colback=lgrey,height=6mm]\textbf{
%Insert link here and add material to cs220
\href{}{Space Travel System {\faGithub}}}
{\(|\) CS253 Course Assignment }
\hfill \textit{(Mar'23-Apr'23)}
\end{tcolorbox}}
\vspace{-2.8mm}
\begin{itemize}
\item  Implemented concepts of Object Oriented Programming of C++ in a Space Travel System(STS) to efficiently manage inter-planetary travel, with automatic initialisation of flights and assigning of commander and astronauts to it.
\item Utilized various Inheritance classes, Virtual functions, Exception handling to all classes for proper functioning.
\item Completed all functionalities starting from registration of travellers to their space travel to respective planets.
\end{itemize}

\vspace{-1.6mm}
{\begin{tcolorbox}[colback=lgrey,height=6mm]\textbf{
\href{https://github.com/Deepanshu18099/Mathematical-Tools-for-Data-Science/tree/main}{Mathematical Tools for Data Science {\faGithub}}}
{\(|\) Stamatics Society, IIT Kanpur}
\hfill \textit{(Apr'22-Jun'22)}
\end{tcolorbox}}
\vspace{-3mm}
\begin{itemize}
\item Learned basic libraries \textbf{Numpy and Pandas} for data analysis, matplotlib based \textbf{Seaborn} for data visualization.
\item sdgaga

\item Learned using Version Control Systems \textbf{Git} and \textbf{Github}, properly for project management.
\end{itemize}

\vspace{-1.6mm}
{\begin{tcolorbox}[colback=lgrey,height=6mm]\textbf{
\href{https://github.com/Deepanshu18099/ACA_FSWD_2022}{Full Stack Web Development {\faGithub}}}
{\(|\) Association for Computing Activities (ACA) Project, IIT Kanpur}
\hfill \textit{(Mar'22-Jun'22)}
\end{tcolorbox}}
\vspace{-3mm}
\begin{itemize}
\item Learned basics of web development, using Bootstrap, Javascript and how to make \textbf{API calls} to server hosted on cloud.
\item Implemented a personal \textbf{portfolio} with \textbf{user registration and authentication}, and added my details to it.
\end{itemize}


\vspace{-3mm}
%\medskip
%{\large \textbf{\begin{tcolorbox}\textsc{Other Projects}\end{tcolorbox}}}
%\begin{itemize}

%\end{itemize

{\begin{tcolorbox}[colback=mygrey,height=6mm]\textbf{\textsc{\large Technical Skills}}\hfill{FamilierWith*} \end{tcolorbox}
}
\begin{itemize}
\itemsep0em
\vspace{-3mm}

\item \textbf{Programming Languages: }C, C++, Python, Javascript*, HTML, CSS, SQL, Verilog HDL*,

\item \textbf{Libraries/Utilities: } Pandas, Numpy, Django, Seaborn*, ReactJS*, Bash, {\LaTeX}, AutoCAD, Adobe Illustrator
\end{itemize}
\medskip
{\large \textbf{\begin{tcolorbox}[colback=mygrey,height=6mm]\textsc{Positions of Responsibility}\end{tcolorbox}}}
\vspace{-3mm}
\begin{itemize}
\item \textbf{Head, Web and App} (Udghosh, IIT Kanpur)
\hfill\hfill(\textit{Jun'23-Ongoing})
\begin{itemize}
\item Leading a 3-tier team of 20+ developers building and maintaining platforms for smooth conduction of the festival.
\item Made WebApps fully from Scratch using \textbf{ReactJs and GSAP} with registration of 6k+ users on website itself
\item Used \textbf{Node package manager} and \textbf{Google-firebase} hosting to host the \href{https://ca.udghosh.org.in}{WebApp \faExternalLink} on the respective domains.
%\item Helped in the \textbf{registration} of more than \textbf{800 students}, aided by other student guides
\end{itemize}
\vspace{1mm}
\item \textbf{Academic Mentor Phy112/115} (Counselling Services)\hfill(\textit{Nov'22-Jul'23})
\begin{itemize}
\item Conducted Institute level remedial classes for 30+ freshmen and also organised doubt session at wing levels.
\item Helped juniors in the subject by clarifying doubts and strengthen their concepts, particularly in Central Forces
%\item Helped in the \textbf{registration} of more than \textbf{800 students}, aided by other student guides
\end{itemize}
\vspace{1mm}
\item \textbf{Organizer, Design} (Udghosh, IIT Kanpur) \hfill\textit{(Aug'22-Oct'22)}
\begin{itemize}
\item Successfully worked with \textbf{Digital design} team for creating \textbf{UX Designs} for Website, for brochure and posters
\item Assisted in conduction of UNOSQ with 3 tier team and subsiquently increased number of participants.

\vspace{-2mm}

%\item Acted as a link between Placement core team, companies and Students during placement process.
\end{itemize}
\vspace{1mm}
\end{itemize}
\begin{tcolorbox}[colback=mygrey,height=6mm]{\textbf{\textsc{\large{Relevant Completed Courses}}}}\hfill{A*-Exceptional Performance}
\end{tcolorbox}
\begin{center}
\begin{tabular}{|p{6cm}|p{6cm}|p{6cm}|}
\hline
Data Structure and Algorithms & Computer Organization & Introduction to Economics\textbf{*}\\
Software Developments and Operations & Modern Cryptology & Introduction to Electronics\\
Discrete Maths for Computer Science & Logic for Computer Science & Probability for Computer Science\\
Fundamentals of Computing &  Linear algebra and ODE \\
\hline
\end{tabular}
\end{center}
\vspace{-2mm}

%\medskip
%\newpage
%\end{itemize}
{\large \textbf{\begin{tcolorbox}[colback=mygrey,height=6mm]\textsc{Extra-Curricular Activities}\end{tcolorbox}}}
\begin{itemize}
\vspace{-2mm}
\item Actively Participating in Coding Contests on Codeforces for 2 months with current best rating of 1269.
\item Bagged 2nd position in \textbf{GUESS-IT-MATE} competetion organised by Finance \& Analytics Club with team of 4 students.
\item Participated in Freshers Dance Showcase by Dance club IITK with a team of 20 students.
\end{itemize}
\end{document}