\documentclass[10pt,a4paper]{extarticle}
%\documentclass[]{file}
\usepackage[a4paper,margin = 0.3in]{geometry}
\usepackage{romannum}
\usepackage{mathtools} 
\usepackage{amsmath} 
\usepackage{fontawesome}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage[super]{nth}
% \usepackage[usenames,dvipsnames]{xcolor}
%...................rahul codes......................
\usepackage{lipsum}
\usepackage{enumitem}
\usepackage{color}
\newlength\boxwid%
\definecolor{mygrey}{rgb}{0.73, 0.73, 0.73}
\definecolor{lgrey}{rgb}{0.9, 0.9,0.9}
\let\oldtextbullet=\textbullet
\def\textbullet{%
    \settowidth{\boxwid}{\ \indent\oldtextbullet\ }%
    \hangindent=\boxwid%
    \oldtextbullet}
    \usepackage{marvosym,array,amsfonts}
\usepackage{array}              %% for adjusting column widths in table
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}     %% new column type
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}       %% new column type
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}      %% new column type
\usepackage{hyperref}
\setlength{\parindent}{0pt}	%% used for setting the no indentation at the beginning of the paragraph
\usepackage{multicol}
\newcommand{\tabitem}{\textbullet~~}
%......................................................
\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!50,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
    }
\begin{document}
\pagenumbering{gobble}
\begin{flushleft}
\noindent {\Huge\textbf{{Deepanshu}}}
\end{flushleft}
\vspace{0pt}
3rd Year Undergraduate  \hfill\href{mailto:deepanshu21@iitk.ac.in}{{\faEnvelope} deepanshu21@iitk.ac.in} \(|\) \href{tel:+917082575299}{ {\faPhone} +917082575299}\\
%\vspace{-2pt}
Department of Computer Science and Engineering \hfill\href{https://github.com/Deepanshu18099}{{\faGithub} Deepanshu18099} \(|\) \href{https://www.linkedin.com/in/deepanshu-yadav-65a1ab223/}{{\faLinkedin} deepanshu-yadav}
\vspace{-6pt}
\\
\vspace{-8pt}
\noindent\rule[0.5ex]{\linewidth}{1pt}
\vspace{-18pt}
{\large \textbf{\begin{tcolorbox}[colback=mygrey,height=6mm]\textsc{Academic Qualifications}\end{tcolorbox}}}
\vspace{-6pt}
\begin{center}
\begin{tabular}{|p{2.4cm}|p{4.2cm}|p{8.5cm}|p{1.8cm}|}
\hline
\centering{\textbf{Year}} & \centering{\textbf{Degree/Certificate}} & \centering{\textbf{Institute}} & \textbf{CPI/$\%$}\\
\hline
\centering{2021} - Present & \centering{B.Tech} & \centering{Indian Institute of Technology Kanpur} & 7.0/10\\
\hline
\centering{2021} & \centering{CBSE(\Romannum{12})} & \centering{Yaduvanshi Shiksha Niketan, Narnaul} & 89.8$\%$\\
\hline
\centering{2019} & \centering{CBSE(\Romannum{10})} & \centering{Yaduvanshi Shiksha Niketan, Narnaul} & 90.6$\%$
\\
\hline
\end{tabular}
\end{center}
\vspace{0mm}
{\large \textbf{\begin{tcolorbox}[colback=mygrey,height=6mm]\textsc{Scholastic Achievements}\end{tcolorbox}}}
\vspace{-2.8mm}
\begin{itemize}
\item Secured \textbf{All India Rank 1040} in \textbf{JEE-Advanced 2021} among 1.4 Lakh candidates, Conducted by IIT Kharagpur.
\item Secured \textbf{All India Rank 2204} in \textbf{JEE-Main 2021} among 10 lakh+ appeared candidates all over India.
\item Recipient of Excellence Scholarship from \textbf{National Talent Search Examination 2019} conducted by \textbf{NCERT}.
\item Scored \textbf{100 percentile} in \textbf{Physics} subject	 in \textbf{JEE-Main 2021} by scoring a maximum possible score 100/100.
\item Among \textbf{State top 1\%} in \textbf{National Standard Examination In Junior Science 2018-2019} conducted by IAPT.
\end{itemize}

\medskip
\vspace{-8mm}

{\large \textbf{\begin{tcolorbox}[colback=mygrey,height=6mm]\textsc{Key Projects}\end{tcolorbox}}}

\vspace{-6mm}
{\begin{tcolorbox}[colback=lgrey,height=6mm]\textbf{
\href{https://github.com/atulyasndrm/Starbugs}{HealthPlusPlus {\faGithub}}}
{\(|\) CS253 Course Project}
\hfill \textit{(Jan'23-Apr'23)}
\end{tcolorbox}}
\vspace{-1.8mm}
\hspace{3mm}\textbf{Mentor}:\emph{ Prof. Indranil Saha (Computer Science and Engineering, IIT Kanpur)}
\begin{itemize}
\item  With a team of 10, Developed an \textbf{automated software} for \textbf{Health Center} of IITK providing its services online.
\item Used rapid development framework \textbf{Django} for back-end and its SQL database, \textbf{HTML, CSS, JavaScript} for front-end.
\item Executed an end-to-end development process from \textbf{SRS} and \textbf{Design} document to {implementation} of automated parts.
\item Collaborated with another team for \textbf{Beta Testing} to identify and resolve the errors within both team’s applications
\end{itemize}


\vspace{-1.6mm}
{\begin{tcolorbox}[colback=lgrey,height=6mm]\textbf{
\href{https://github.com/Deepanshu18099/CS220-Project}{CSE-Bubble Processor {\faGithub}}}
{\(|\) CS220 Course Project }
\hfill \textit{(Jan'23-Apr'23)}
\end{tcolorbox}}
\vspace{-2mm}
\hspace{3mm}\textbf{Mentor}:\emph{ Prof. Urbi Chatterjee (Computer Science and Engineering, IIT Kanpur)}
\begin{itemize}
\item Framed a \textbf{single-cycle processor}, including \textbf{Opcode} design, \textbf{data path} implementation and \textbf{control path} development.
\item Implemented \textbf{ALU} and \textbf{Control Unit} in the top-down approach to develop different modules for different Opcodes.
\item Utilized \textbf{MIPS-32} code for \textbf{Bubble Sort}, converting it to machine code and storing output in data-memory \textbf{VEDA}.
\end{itemize}

\vspace{-1.6mm}
{\begin{tcolorbox}[colback=lgrey,height=6mm]\textbf{
%Insert link here and add material to cs220
\href{https://github.com/Deepanshu18099/Space-Travel-System.git}{Space Travel System {\faGithub}}}
{\(|\) CS253 Course-Assignment }
\hfill \textit{(Mar'23-Apr'23)}
\end{tcolorbox}}
\vspace{-3mm}
\begin{itemize}
\item  Implemented concepts of \textbf{Object Oriented Programming} of C++ in a Space Travel System(STS) to efficiently manage interplanetary travel, with automatic initialization of flights and assignment of commanders and astronauts to it.
\item Utilized various \textbf{Inheritance classes}, \textbf{Virtual functions}, \textbf{Exception handling} to all classes for proper functioning.
\item Completed all functionalities starting from registration of travelers to their space-travel tickets for respective planets.
\end{itemize}

\vspace{-1.6mm}
{\begin{tcolorbox}[colback=lgrey,height=6mm]\textbf{
\href{https://github.com/Deepanshu18099/Mathematical-Tools-for-Data-Science/tree/main}{Mathematical Tools for Data Science {\faGithub}}}
{\(|\) Stamatics Society, IIT Kanpur}
\hfill \textit{(Apr'22-Jun'22)}
\end{tcolorbox}}
\vspace{-3.2mm}
\begin{itemize}
\item Learned basics of \textbf{Numpy and Pandas} libraries for data analysis, \textbf{matplotlib} based \textbf{Seaborn} for data visualization.
\item Applied Seaborn on a dataset of salaries of employees and visualized the trends in their Overtime benefits. 
\end{itemize}

\vspace{-1.6mm}
{\begin{tcolorbox}[colback=lgrey,height=6mm]\textbf{
\href{https://github.com/Deepanshu18099/ACA_FSWD_2022}{Full Stack Web Development {\faGithub}}}
{\(|\) Association for Computing Activities (ACA) Project, IIT Kanpur}
\hfill \textit{(Apr'22-Jun'22)}
\end{tcolorbox}}
\vspace{-3.2mm}
\begin{itemize}
\item Learned basics of web development, using \textbf{Bootstrap}, \textbf{Javascript}, and how to make \textbf{API calls} to a server on cloud.
\item Implemented a personal \textbf{portfolio} with \textbf{user registration and authentication}, and added my details to it.
\end{itemize}

\vspace{-3mm}
%\medskip
%{\large \textbf{\begin{tcolorbox}\textsc{Other Projects}\end{tcolorbox}}}
%\begin{itemize}

%\end{itemize

{\begin{tcolorbox}[colback=mygrey,height=6mm]\textbf{\textsc{\large Technical Skills}}\end{tcolorbox}
}
\begin{itemize}
\itemsep0em
\vspace{-3mm}

\item \textbf{Programming Languages: }C, C++, Python, Javascript, HTML, CSS, SQL, Verilog HDL

\item \textbf{Libraries/Utilities: } Pandas, Numpy, Django, Seaborn, ReactJS, Bash, {\LaTeX}, AutoCAD, Adobe Illustrator
\end{itemize}
\medskip
{\large \textbf{\begin{tcolorbox}[colback=mygrey,height=6mm]\textsc{Positions of Responsibility}\end{tcolorbox}}}
\vspace{-3.5mm}
\begin{itemize}
\item \textbf{Head, Web and App} (Udghosh, IIT Kanpur)
\hfill\hfill(\textit{Jun'23-Present})
\begin{itemize}
\item Leading a \textbf{3-tier team} of 20+ developers building and maintaining platforms for the smooth conduction of festival.
\item Made WebApps fully from Scratch using \textbf{ReactJs and GSAP} with registration of 6k+ users on the website itself.
\item Used \textbf{Node package manager} and \textbf{Google-firebase} hosting to host the \href{https://ca.udghosh.org.in}{WebApps \faExternalLink} on the respective domains.
%\item Helped in the \textbf{registration} of more than \textbf{800 students}, aided by other student guides
\end{itemize}

\vspace{0.5mm}
\item \textbf{Organizer, Design \& Videography} (Udghosh, IIT Kanpur) \hfill\textit{(Aug'22-Oct'22)}
\begin{itemize}
\item Successfully worked with \textbf{Digital design} team for creating \textbf{UX Designs} for Website, for brochure and posters.
\item Assisted in conducting UNOSQ with 3 tier team and subsequently increased the number of participants.

\vspace{-2.5mm}

%\item Acted as a link between the Placement core team, companies, and Students during the placement process.
\end{itemize}
\vspace{1mm}
\end{itemize}
\begin{tcolorbox}[colback=mygrey,height=6mm]{\textbf{\textsc{\large{Relevant Completed Courses}}}}\hfill{A*-Exceptional Performance}
\end{tcolorbox}
\vspace{-2mm}
\begin{center}
\begin{tabular}{|p{6cm}|p{6cm}|p{6cm}|}
\hline
Data Structure and Algorithms & Computer Organization & Introduction to Economics\textbf{*}\\
Software Developments and Operations & Modern Cryptology & Introduction to Electronics\\
Discrete Maths for Computer Science & Logic for Computer Science & Probability for Computer Science\\
Fundamentals of Computing &  Linear Algebra and ODE & Algorithm-II(Ongoing)\\
\hline
\end{tabular}
\end{center}
\vspace{-3mm}
%\medskip
%\newpage
%\end{itemize}
{\large \textbf{\begin{tcolorbox}[colback=mygrey,height=6mm]\textsc{Extra-Curricular Activities}\end{tcolorbox}}}
\begin{itemize}
\vspace{-3.5mm}
\item Was Academic mentor of course Phy112/115 for session 2021-22, mentoring 30 freshman students in Academic difficulties.
\item Bagged 2nd position in \textbf{GUESS-IT-MATE} competetion organised by Finance \& Analytics Club with team of 4 students.
\item Active participation in Inter Hall technical competition \textbf{Takneek'23}, securing overall 2nd position among other halls.
\end{itemize}
\end{document}

\vspace{1.5mm}
\item \textbf{Academic Mentor} (Counselling Service, IIT Kanpur)\hfill(\textit{Nov'22-Jul'23})
\begin{itemize}
\item Conducted \textbf{Institute level remedial classes} of Phy112/115 for 30+ freshmen and also organised wing-level session.
\item Helped juniors in the subject by clarifying doubts and strengthening their concepts, particularly in Central Forces.
%\item Helped in the \textbf{registration} of more than \textbf{800 students}, aided by other student guides
\end{itemize}